Evaluating the Supportive Effect of Feature Selection Methods on Machine Learning Models in Monitoring Forest Health Using Hyperspectral Remote Sensing Data

### 2020-04-07 docs/00-manuscripts/ieee/ieee-manuscript.tex
A.B. review: Conclusion wording

% RQ2: Does combining feature sets have an substantial effect on predictive performance?
% RQ1: Do different environmental feature sets show differences in performance when modeling defoliation at trees?
The creation of derived feature sets did not contribute to an improvement in model performance.
In contrast, dataset VI showed a substantial worse performance than the dataset with the original features (HR).
Combining feature sets did not show a substantial improvement on predictive performance.

@@

% What about the general potential of analyzing defol with hyperspectral data?
The potential of predicting defoliation for single trees with the given toolset of this study was rather limited, seen on the average error of 27\%. 
However, with better training data covering more variety of the response variable, performance could be highly improved in future studies.

>>>>

% RQ2: Does combining feature sets have an substantial effect on predictive performance?
% RQ1: Do different environmental feature sets show differences in performance when modeling defoliation at trees?
The creation of derived feature sets did not contribute to an improvement in model performance.
In contrast, dataset VI showed a substantially poorer performance than the dataset with the original features (HR).
Combining feature sets did not show a substantial improvement on predictive performance.

@@

% What about the general potential of analyzing defol with hyperspectral data?
The potential of predicting defoliation for single trees as conducted in this study was rather limited with an average RMSE of 27 p.p..
We suggest that training data covering a wider range of defoliation values in a larger number of forest plantations would further improve the proposed models and result in more generalizable monitoring algorithms.
